A survey of HTTP caching options on the open Web

### 2015-01-13 sanity/paper1.tex
R:G:HTTP footnote
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@973 43ef1190-90fd-4dd7-a769-d0121f02b80e

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\todo{footnote} to the Comprehensive Perl Archive
Network. We recorded whether the conditional request showed that the
BTC data were still fresh, and if it was, we retrieved the current
data, as we had not couple the headers to the body in our original
retrieval.

>>>>

Then, the first request would be made, and a selection of the
resulting HTTP headers recorded in an per-host NQuads file. For this
purpose, we developed and released a module
RDF::Generator::HTTP\footnote{https://metacpan.org/release/KJETILK/RDF-Generator-HTTP-0.003}
to the Comprehensive Perl Archive Network. We recorded whether the
conditional request showed that the BTC data were still fresh, and if
it was, we retrieved the current data, as we had not couple the
headers to the body in our original retrieval.
